\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage[os=win]{menukeys}

\begin{document}

    \title{VoxelGame User Manual}
    \author{pershingthesecond}

    \maketitle
    \newpage

    \tableofcontents
    \newpage


    \section{Welcome!}\label{sec:welcome!}

    Thank you for downloading VoxelGame.
    Currently there is some basic information in this manual, but it will be continuously expanded.
    VoxelGame is a project I sometimes work on to learn new things and have fun programming, so do not expect too much, especially on the performance side.


    \section{Versions}\label{sec:versions}

    \begin{enumerate}
        \item[1.0.0] The First Release
        \item[1.1.0] The World Update
        \item[1.2.0] The Block Update
    \end{enumerate}


    \section{Controls}\label{sec:controls}

    \subsection{General}\label{subsec:general}
    \begin{itemize}
        \item Press \keys{\esc} to save and close the game.
        \item Press \keys{F12} to take a screenshot.
        It will be saved to \directory{/My Pictures/VoxelGame}.
    \end{itemize}

    \subsection{Movement}\label{subsec:movement}
    \begin{itemize}
        \item Classical movement using \keys{W}\keys{A}\keys{S}\keys{D}, hold \keys{\shift} to sprint.
        \item Press \keys{\SPACE} to jump.
        \item Use the mouse to look around.
        The sensitivity can be changed in the config file, but currently the mouse movement is a bit strange.
    \end{itemize}

    \subsection{World Interaction}\label{subsec:world-interaction}
    \begin{itemize}
        \item Use \textit{Left Mouse Button} to destroy blocks and \textit{Right Mouse Button} to place them.
        \item Some blocks allow to interact with them by clicking \textit{Right Mouse Button}.
        To place a block instead of interacting, hold the \keys{\ctrl} button.
        \item Press \keys{Num Plus} and \keys{Num Minus} to cycle through all available blocks.
        \item Press \keys{R} to switch between block and liquid mode.
    \end{itemize}

    \subsection{Debug}\label{subsec:debug}
    \begin{itemize}
        \item Press \keys{K} to switch to Wireframe Mode.
    \end{itemize}

\end{document}
